Learning and comparing functional connectomes between populations

### 2012-12-30 paper.tex
typos

% Define terms
By ``functional connectome'', here we specifically denote a graph
representing functional interactions in the brain, where the term
``graph'' is taken in its mathematical sens: a set of \emph{nodes}
connected together by \emph{edges}. A graph can be weighted or not, and
is completely equivalent to its \emph{adjacency matrix}, a symmetric
matrix tabulating the connection weights between each pair of nodes.
Functional-connectivity graphs can be used to represent evoked activity,
as in task-response studies \cite{mcintosh2000}, as well as
task-independent ongoing activity that is present in the background
during task and often studies in so-called \emph{resting-state}
experiments \cite{raichle2010}. Another important notion that arises from
the study of distributed modes of brain function is that of specialized
functional networks\footnote{In neuroimaging, the term network is
sometimes used to denote a graph of brain function. To disambiguate the
notion of segregated spatial mode \cite{fox2005} from that of
connectivity graphs, we will purposely restrict its usage in this
paper.}. With our definition of the functional connection, functional
networks are not directly building blocks of the connectome but appears
as a consequence of the graphical structure
\cite{varoquaux2010c,varoquaux2012}.

>>>>

% Define terms
By ``functional connectome'', here we specifically denote a graph
representing functional interactions in the brain, where the term
``graph'' is taken in its mathematical sens: a set of \emph{nodes}
connected together by \emph{edges}. A graph can be weighted or not, and
is completely equivalent to its \emph{adjacency matrix}, a symmetric
matrix tabulating the connection weights between each pair of nodes.
Functional-connectivity graphs can be used to represent evoked activity,
as in task-response studies \cite{mcintosh2000}, as well as
task-independent ongoing activity that is present in the background
during task and often studies in so-called \emph{resting-state}
experiments \cite{raichle2010}. Another important notion that arises from
the study of distributed modes of brain function is that of specialized
functional networks\footnote{In neuroimaging, the term network is
sometimes used to denote a graph of brain function. To disambiguate the
notion of segregated spatial mode \cite{fox2005} from that of
connectivity graphs, we will purposely restrict its usage in this
paper.}. With our definition of the functional connectome, functional
networks are not directly building blocks of the connectome but appear
as a consequence of the graphical structure
\cite{varoquaux2010c,varoquaux2012}.
